\bf Title here

### 2020-08-31 paper/paper.Rmd
more changes of the section title, add new section on animated plots

## Data structure

@@

## Plot constructions

@@

### How hard is the optimiser working

@@

### Examining the interpolation

@@

@@

## A more complex example: Interruption

@@

## Another example: Polish

@@

## A comprehensive example of diagnosing a noisy index function

@@

### Explore index value

@@

### Explore searching space

>>>>

## Data structure for diagnostics

@@

@@

## Check how hard the optimiser is working

@@

## Examining the interpolation progress

@@

## Animating the diagnostic plots

all the plots above can be animated if wanted - importance is how the data is moving around

show an example of some snap shots  of the animation and provide a link... for animated pca plot

## The tour looking at itself

show the path of the tour on a sphere. (full data dimension animation...)

include the tour animation (geozoo)

@@

## A problem of not monotonic

@@

## Close but not close enough

@@

## Seeing the signal in the noise

@@

@@

### 2020-08-31 paper/paper.tex
more changes of the section title, add new section on animated plots

\hypertarget{data-structure}{%
\subsection{Data structure}\label{data-structure}}

@@

\hypertarget{plot-constructions}{%
\subsection{Plot constructions}\label{plot-constructions}}

@@

\hypertarget{how-hard-is-the-optimiser-working}{%
\subsubsection{How hard is the optimiser
working}\label{how-hard-is-the-optimiser-working}}

@@

\hypertarget{examining-the-interpolation}{%
\subsubsection{Examining the
interpolation}\label{examining-the-interpolation}}

@@

@@

{[}a paragraph that motivate the section: these optimisers are suspect
to have problem, here is how we use the diag plot to diagnose them. {]}

Below we will present several examples of diagnosing different aspects
of the projection pursuit optimisation. We will present more examples
that can help us to understand the algorithm and parameter choice:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \ldots{}
\item
  \ldots{}
\item
  \ldots{}
\item
  \ldots{}
\end{enumerate}

Remember the research question we raised earlier, the purpose of visual
diagnostics is to understand:

\begin{itemize}
\item
  Whether the algorithm has successfully found the maximum and how the
  index value changes throughout the algorithm?
\item
  How does the searching space look like, that is, geometrically, where
  are the projection bases located in the space?
\end{itemize}

(mention optim difficulties and split the simulated data section into
the examples!!!)

@@

We simulate some random variables of size 1000 with different
structures. \texttt{x1}, \texttt{x8}, \texttt{x9} and \texttt{x10} are
simulated from normal distribution with zero mean and variance of one as
in equation \ref{eq:sim-norm}. When using projection pursuit to explore
the data structure based on its departure from normality, the entry in
the projection basis for these variables should be close to zero in
theory. \texttt{x2} to \texttt{x7} are mixture of normal distributions
with different weights and locations. Equation \ref{eq:sim-x2} to
\ref{eq:sim-x7} outlines the distribution where each variable is
simulated from and Figure \ref{origin-data} shows the histogram of each
variable except \texttt{x3}. All the variables are then scaled to have
unit variance before running the projection pursuit.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/origin-data-1.pdf}
\caption{\label{origin-data} The distribution of simulated data except
x3}
\end{figure}

{[}I notice that in the implementation the loop index for interpolation
starts from 0 rather than 1. Need more investigation to see if it is
easy to change it to 1 or we will have to change the definition of the
data structure.{]}

\hypertarget{a-more-complex-example-interruption}{%
\subsection{A more complex example:
Interruption}\label{a-more-complex-example-interruption}}

@@

\hypertarget{another-example-polish}{%
\subsection{Another example: Polish}\label{another-example-polish}}

@@

\hypertarget{a-comprehensive-example-of-diagnosing-a-noisy-index-function}{%
\subsection{A comprehensive example of diagnosing a noisy index
function}\label{a-comprehensive-example-of-diagnosing-a-noisy-index-function}}

@@

\hypertarget{explore-index-value}{%
\subsubsection{Explore index value}\label{explore-index-value}}

@@

\hypertarget{explore-searching-space}{%
\subsubsection{Explore searching space}\label{explore-searching-space}}

>>>>

\hypertarget{data-structure-for-diagnostics}{%
\subsection{Data structure for
diagnostics}\label{data-structure-for-diagnostics}}

@@

@@

\hypertarget{check-how-hard-the-optimiser-is-working}{%
\subsection{Check how hard the optimiser is
working}\label{check-how-hard-the-optimiser-is-working}}

@@

\hypertarget{examining-the-interpolation-progress}{%
\subsection{Examining the interpolation
progress}\label{examining-the-interpolation-progress}}

@@

\hypertarget{animating-the-diagnostic-plots}{%
\subsection{Animating the diagnostic
plots}\label{animating-the-diagnostic-plots}}

all the plots above can be animated if wanted - importance is how the
data is moving around

show an example of some snap shots of the animation and provide a
link\ldots{} for animated pca plot

\hypertarget{the-tour-looking-at-itself}{%
\subsection{The tour looking at
itself}\label{the-tour-looking-at-itself}}

show the path of the tour on a sphere. (full data dimension
animation\ldots{})

include the tour animation (geozoo)

@@

The three algorithms introduced in Section \ref{tour} have experienced
several practical issues in application. {[}initial problems with tourr
optim, 2-3 sentences{]}. These issues can be studied and investigated
using the diagnostic plots constructed above.

@@

Random variables with different structures has been simulated and the
distribution of each is presented in Equation \ref{eq:sim-norm} to
\ref{eq:sim-x7}. Variable \texttt{x1}, \texttt{x8}, \texttt{x9} and
\texttt{x10} are normal distributed with zero mean and unit variance and
\texttt{x2} to \texttt{x7} are mixture of normal distributions with
different weights and locations. Figure \ref{origin-data} plots the
histogram of each variable except \texttt{x3}. The mixture variables are
scaled to have unit variance before running the projection pursuit.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/origin-data-1.pdf}
\caption{\label{origin-data} The histogram of simulated selected
variables.}
\end{figure}

\hypertarget{a-problem-of-not-monotonic}{%
\subsection{A problem of not
monotonic}\label{a-problem-of-not-monotonic}}

@@

\hypertarget{close-but-not-close-enough}{%
\subsection{Close but not close
enough}\label{close-but-not-close-enough}}

@@

\hypertarget{seeing-the-signal-in-the-noise}{%
\subsection{Seeing the signal in the
noise}\label{seeing-the-signal-in-the-noise}}

@@

@@
